---
output: github_document
#runtime: shiny
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# nhanesGraph

<!-- badges: start -->
[![R-CMD-check](https://github.com/minjee-kim/nhanesGraph/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/minjee-kim/nhanesGraph/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

nhanesGraph is a package that provides an accessible and interactive way for users to export NHANES data as well as view data trends via Shiny package. This package is an extension of the [RNHANES](https://cran.r-project.org/web/packages/RNHANES/vignettes/introduction.html) package created by Herb Susmann. 

## Installation

You can install the development version of nhanesGraph from [GitHub](https://github.com/minjee-kim/nhanesGraph) with:

``` r
# install.packages("devtools")
devtools::install_github("minjee-kim/nhanesGraph")
```

## Data Loading via nhanes_table function

From the console, the NHANES data can be accessed via nhanes_table() function by specifying the cycle (or a specific year), file name, and whether to include demographic information for the samples in the data in the loaded data. The demographics parameter is False by default. The recode parameter allows users to load the data with descriptive categorical variables. By default, recode is False. 

```{r example}
library(nhanesGraph)

head(nhanes_table("2008", "EPH", demographics = T, recode = F))

```
### File Search 

In order to specify the year and file inputs in the nhanes_table function, users can explore the NHANES files with nGraph_search Shiny app. The Shiny app can be launched with the folloing code: 

```{r, eval = F}
nGraph_search()
```

## Variable Visualization


