---
output: github_document
#runtime: shiny
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

CODECOV_TOKEN=52721b18-0aff-4ed8-b515-2c348f7cc091

# nhanesGraph

<!-- badges: start -->
[![R-CMD-check](https://github.com/minjee-kim/nhanesGraph/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/minjee-kim/nhanesGraph/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

nhanesGraph is a package that provides an accessible and interactive way for users to export NHANES data as well as view data trends via Shiny package. This package is an extension of the [RNHANES](https://cran.r-project.org/web/packages/RNHANES/vignettes/introduction.html) package created by Herb Susmann. 

## Installation

You can install the development version of nhanesGraph from [GitHub](https://github.com/minjee-kim/nhanesGraph) with:

``` r
# install.packages("devtools")
devtools::install_github("minjee-kim/nhanesGraph")
```

## Example

Users are able to search the NHANES file of interest via nGraph_search() Shiny app. 



For a console command, users can access nhanes_table function 

```{r example}
library(nhanesGraph)

#nGraph_search()
head(nhanes_table("2007-2008", "EPH"))

```

There will be a plot that looks much nicer than this :)

