---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nhanesGraphR

<!-- badges: start -->
<!-- badges: end -->

The goal of nhanesGraphR is to provide an interactive graphical tools for the users to access more easily. This package utilizes RNHANES, nhanesA, and Shiny packages. 


# Intermediate Project Update
So far, I have a function that retrieves data from the CDC website with more flexible commands and a function that outputs the data into a publication ready table. 

To do: \
make the vignette look much nicer \
finish writing the function that outputs publication ready tables using the sjPlot package <br>
add variable search via nhanesA  <br>
finish the function for interactive plots \
finish documentation <br>
make the nhnaes_table to allow:  
  \ 1. make the input case insensitive \
  \ 2. downloading without year specification \
  \ 3. if type and variables do not agree (variables specified by the user are not in the specified type), ask if the user wants both (display yes or no)


## Installation

You can install the development version of nhanesGraphR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("minjee-kim/nhanesGraph")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nhanesGraphR)

Ngraph_table("2001 - 2010", "exam")
```

There will be a plot that looks much nicer than this :)

```{r pressure, echo = FALSE}
plot(pressure)
```

